---
title: "Initial Data Processing"
output: html_notebook
---

# Install Necessary Packages

```{r}
#install.packages("tidyr")
library(tidyr)

#install.packages("dplyr")
library(dplyr)
```

# Script Notes

- Each of the 24 species included in the final version of the application are listed in alphabetical order
- For each species, the raw data files generated by IntaRNA were loaded in from a folder and stitched together. These files are provided in the Github repository.  
- The final output for each species is an energy table with the transcripts of the species as rows and the human miRNAs as columns. The cells of this table contain the IntaRNA energy scores
- For each species, the success of the IntaRNA algorithm was checked - to make sure that all 630 human miRNAs screened showed up in the energy table, and that all or nearly all of the transcripts in each particular species were screened (on rare occasions, IntaRNA did not make predictions for a certain transcript. So long as the number of these transcripts was small relative to the total - less than 1% - this was deemed acceptable). The fraction of transcripts screened is listed next to each species. 

# Species: Achromobacter xylosoxidans (6786/6786 transcripts)
First load in data files (27):
```{r}
AX_Files <- vector(mode = "list", length = 27)
AX_File_List <- list.files(path = "./Output_Files/CF/AX_A8", pattern = ".txt")

setwd("./Output_Files/CF/AX_A8")

for (i in 1:length(AX_Files)) {
  AX_Files[[i]] <- read.table(AX_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(AX_Files)
```

Then merge those data files into a single large table:
```{r}
AX_Data <- rbind(AX_Files[[1]], AX_Files[[2]], AX_Files[[3]], AX_Files[[4]], AX_Files[[5]], AX_Files[[6]], AX_Files[[7]], AX_Files[[8]], AX_Files[[9]], AX_Files[[10]], AX_Files[[11]], AX_Files[[12]], AX_Files[[13]], AX_Files[[14]], AX_Files[[15]], AX_Files[[16]], AX_Files[[17]], AX_Files[[18]], AX_Files[[19]], AX_Files[[20]], AX_Files[[21]], AX_Files[[22]], AX_Files[[23]], AX_Files[[24]], AX_Files[[25]], AX_Files[[26]], AX_Files[[27]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
AX_Data_VF <- AX_Data[, -c(7,8)]
colnames(AX_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
AX_Data_VF <- distinct(AX_Data_VF)

AX_Energy <- spread(AX_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(AX_Energy) <- AX_Energy[,1]
AX_Energy <- AX_Energy[,-1]
View(AX_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(AX_Energy) #630/630 miRNAs in raw FASTA file
nrow(AX_Energy) #6786/6786 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(AX_Energy, "./Exported_Tables/AX_Energy.csv")
```


# Species: Acinetobacter baumannii (3811/3814 transcripts)
First load in data files (16):
```{r}
AB_Files <- vector(mode = "list", length = 16)
AB_File_List <- list.files(path = "./Output_Files/ESKAPE/AB_AYE", pattern = ".txt")

setwd("./Output_Files/ESKAPE/AB_AYE")

for (i in 1:length(AB_Files)) {
  AB_Files[[i]] <- read.table(AB_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(AB_Files)
```

Then merge those data files into a single large table:
```{r}
AB_Data <- rbind(AB_Files[[1]], AB_Files[[2]], AB_Files[[3]], AB_Files[[4]], AB_Files[[5]], AB_Files[[6]], AB_Files[[7]], AB_Files[[8]], AB_Files[[9]], AB_Files[[10]], AB_Files[[11]], AB_Files[[12]], AB_Files[[13]], AB_Files[[14]], AB_Files[[15]], AB_Files[[16]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
AB_Data_VF <- AB_Data[, -c(7,8)]
colnames(AB_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
AB_Data_VF <- distinct(AB_Data_VF)

AB_Energy <- spread(AB_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(AB_Energy) <- AB_Energy[,1]
AB_Energy <- AB_Energy[,-1]
View(AB_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(AB_Energy) #630/630 miRNAs in raw FASTA file
nrow(AB_Energy) #3811/3814 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(AB_Energy, "./Exported_Tables/AB_Energy.csv")
```


# Species: Aspergillus fumigatus (9630/9632 transcripts)

First load in data files (39):
```{r}
AF_Files <- vector(mode = "list", length = 39)
AF_File_List <- list.files(path = "./Output_Files/AF/Complete", pattern = ".txt")

setwd("./Output_Files/AF/Complete")

for (i in 1:length(AF_Files)) {
  AF_Files[[i]] <- read.table(AF_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(AF_Files)
```

Then merge those data files into a single large table:
```{r}
AF_Data <- rbind(AF_Files[[1]], AF_Files[[2]], AF_Files[[3]], AF_Files[[4]], AF_Files[[5]], AF_Files[[6]], AF_Files[[7]], AF_Files[[8]], AF_Files[[9]], AF_Files[[10]], AF_Files[[11]], AF_Files[[12]], AF_Files[[13]], AF_Files[[14]], AF_Files[[15]], AF_Files[[16]], AF_Files[[17]], AF_Files[[18]], AF_Files[[19]], AF_Files[[20]], AF_Files[[21]], AF_Files[[22]], AF_Files[[23]], AF_Files[[24]], AF_Files[[25]], AF_Files[[26]], AF_Files[[27]], AF_Files[[28]], AF_Files[[29]], AF_Files[[30]], AF_Files[[31]], AF_Files[[32]], AF_Files[[33]], AF_Files[[34]], AF_Files[[35]], AF_Files[[36]], AF_Files[[37]], AF_Files[[38]], AF_Files[[39]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
AF_Data_VF <- AF_Data[, -c(7,8)]
colnames(AF_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
AF_Data_VF <- distinct(AF_Data_VF)

AF_Energy <- spread(AF_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(AF_Energy) <- AF_Energy[,1]
AF_Energy <- AF_Energy[,-1]
View(AF_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(AF_Energy) #630/630 miRNAs in raw FASTA file
nrow(AF_Energy) #9630/9632 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(AF_Energy, "./Exported_Tables/AF_Energy.csv")
```


# Species: Bacteroides fragilis (4214/4223 transcripts)
First load in data files (17):
```{r}
BF_Files <- vector(mode = "list", length = 17)
BF_File_List <- list.files(path = "./Output_Files/BF", pattern = ".txt")

setwd("./Output_Files/BF")

for (i in 1:length(BF_Files)) {
  BF_Files[[i]] <- read.table(BF_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(BF_Files)
```

Then merge those data files into a single large table:
```{r}
BF_Data <- rbind(BF_Files[[1]], BF_Files[[2]], BF_Files[[3]], BF_Files[[4]], BF_Files[[5]], BF_Files[[6]], BF_Files[[7]], BF_Files[[8]], BF_Files[[9]], BF_Files[[10]], BF_Files[[11]], BF_Files[[12]], BF_Files[[13]], BF_Files[[14]], BF_Files[[15]], BF_Files[[16]], BF_Files[[17]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
BF_Data_VF <- BF_Data[, -c(7,8)]
colnames(BF_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
BF_Data_VF <- distinct(BF_Data_VF)

BF_Energy <- spread(BF_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(BF_Energy) <- BF_Energy[,1]
BF_Energy <- BF_Energy[,-1]
View(BF_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(BF_Energy) #630/630 miRNAs in raw FASTA file
nrow(BF_Energy) #4214/4223 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(BF_Energy, "./Exported_Tables/BF_Energy.csv")
```



# Species: Burkholderia cenocepacia (7314/7314 transcripts)
First load in data files (30):
```{r}
BC_Files <- vector(mode = "list", length = 30)
BC_File_List <- list.files(path = "./Output_Files/BC", pattern = ".txt")

setwd("./Output_Files/BC")

for (i in 1:length(BC_Files)) {
  BC_Files[[i]] <- read.table(BC_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(BC_Files)
```

Then merge those data files into a single large table:
```{r}
BC_Data <- rbind(BC_Files[[1]], BC_Files[[2]], BC_Files[[3]], BC_Files[[4]], BC_Files[[5]], BC_Files[[6]], BC_Files[[7]], BC_Files[[8]], BC_Files[[9]], BC_Files[[10]], BC_Files[[11]], BC_Files[[12]], BC_Files[[13]], BC_Files[[14]], BC_Files[[15]], BC_Files[[16]], BC_Files[[17]], BC_Files[[18]], BC_Files[[19]], BC_Files[[20]], BC_Files[[21]], BC_Files[[22]], BC_Files[[23]], BC_Files[[24]], BC_Files[[25]], BC_Files[[26]], BC_Files[[27]], BC_Files[[28]], BC_Files[[29]], BC_Files[[30]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
BC_Data_VF <- BC_Data[, -c(7,8)]
colnames(BC_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
BC_Data_VF <- distinct(BC_Data_VF)

BC_Energy <- spread(BC_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(BC_Energy) <- BC_Energy[,1]
BC_Energy <- BC_Energy[,-1]
View(BC_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(BC_Energy) #630/630 miRNAs in raw FASTA file
nrow(BC_Energy) #7314/7314 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(BC_Energy, "./Exported_Tables/BC_Energy.csv")
```

# Species: Burkholderia multivorans (6403/6412 transcripts)
First load in data files (26):
```{r}
BM_Files <- vector(mode = "list", length = 26)
BM_File_List <- list.files(path = "./Output_Files/CF/BM_Tohoku", pattern = ".txt")

setwd("./Output_Files/CF/BM_Tohoku")

for (i in 1:length(BM_Files)) {
  BM_Files[[i]] <- read.table(BM_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(BM_Files)
```

Then merge those data files into a single large table:
```{r}
BM_Data <- rbind(BM_Files[[1]], BM_Files[[2]], BM_Files[[3]], BM_Files[[4]], BM_Files[[5]], BM_Files[[6]], BM_Files[[7]], BM_Files[[8]], BM_Files[[9]], BM_Files[[10]], BM_Files[[11]], BM_Files[[12]], BM_Files[[13]], BM_Files[[14]], BM_Files[[15]], BM_Files[[16]], BM_Files[[17]], BM_Files[[18]], BM_Files[[19]], BM_Files[[20]], BM_Files[[21]], BM_Files[[22]], BM_Files[[23]], BM_Files[[24]], BM_Files[[25]], BM_Files[[26]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
BM_Data_VF <- BM_Data[, -c(7,8)]
colnames(BM_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
BM_Data_VF <- distinct(BM_Data_VF)

BM_Energy <- spread(BM_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(BM_Energy) <- BM_Energy[,1]
BM_Energy <- BM_Energy[,-1]
View(BM_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(BM_Energy) #630/630 miRNAs in raw FASTA file
nrow(BM_Energy) #6403/6412 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(BM_Energy, "./Exported_Tables/BM_Energy.csv")
```


# Species: Candida albicans (6030/6030 transcripts)
First load in data files (24):
```{r}
CA_Files <- vector(mode = "list", length = 24)
CA_File_List <- list.files(path = "./Output_Files/CA", pattern = ".txt")

setwd("./Output_Files/CA")

for (i in 1:length(CA_Files)) {
  CA_Files[[i]] <- read.table(CA_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(CA_Files)
```

Then merge those data files into a single large table:
```{r}
CA_Data <- rbind(CA_Files[[1]], CA_Files[[2]], CA_Files[[3]], CA_Files[[4]], CA_Files[[5]], CA_Files[[6]], CA_Files[[7]], CA_Files[[8]], CA_Files[[9]], CA_Files[[10]], CA_Files[[11]], CA_Files[[12]], CA_Files[[13]], CA_Files[[14]], CA_Files[[15]], CA_Files[[16]], CA_Files[[17]], CA_Files[[18]], CA_Files[[19]], CA_Files[[20]], CA_Files[[21]], CA_Files[[22]], CA_Files[[23]], CA_Files[[24]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
CA_Data_VF <- CA_Data[, -c(7,8)]
colnames(CA_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
CA_Data_VF <- distinct(CA_Data_VF)

CA_Energy <- spread(CA_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(CA_Energy) <- CA_Energy[,1]
CA_Energy <- CA_Energy[,-1]
View(CA_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(CA_Energy) #630/630 miRNAs in raw FASTA file
nrow(CA_Energy) #6030/5155 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(CA_Energy, "./Exported_Tables/CA_Energy.csv")
```

# Species: Clostridium difficile (3834/3834 transcripts)
First load in data files (16):
```{r}
CD_Files <- vector(mode = "list", length = 16)
CD_File_List <- list.files(path = "./Output_Files/CD", pattern = ".txt")

setwd("./Output_Files/CD")

for (i in 1:length(CD_Files)) {
  CD_Files[[i]] <- read.table(CD_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(CD_Files)
```

Then merge those data files into a single large table:
```{r}
CD_Data <- rbind(CD_Files[[1]], CD_Files[[2]], CD_Files[[3]], CD_Files[[4]], CD_Files[[5]], CD_Files[[6]], CD_Files[[7]], CD_Files[[8]], CD_Files[[9]], CD_Files[[10]], CD_Files[[11]], CD_Files[[12]], CD_Files[[13]], CD_Files[[14]], CD_Files[[15]], CD_Files[[16]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
CD_Data_VF <- CD_Data[, -c(7,8)]
colnames(CD_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
CD_Data_VF <- distinct(CD_Data_VF)

CD_Energy <- spread(CD_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(CD_Energy) <- CD_Energy[,1]
CD_Energy <- CD_Energy[,-1]
View(CD_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(CD_Energy) #630/630 miRNAs in raw FASTA file
nrow(CD_Energy) #3834/3834 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(CD_Energy, "./Exported_Tables/CD_Energy.csv")
```

# Species: Clostridium perfringens (2855/2855 transcripts)
First load in data files (12):
```{r}
CP_Files <- vector(mode = "list", length = 12)
CP_File_List <- list.files(path = "./Output_Files/CP", pattern = ".txt")

setwd("./Output_Files/CP")

for (i in 1:length(CP_Files)) {
  CP_Files[[i]] <- read.table(CP_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(CP_Files)
```

Then merge those data files into a single large table:
```{r}
CP_Data <- rbind(CP_Files[[1]], CP_Files[[2]], CP_Files[[3]], CP_Files[[4]], CP_Files[[5]], CP_Files[[6]], CP_Files[[7]], CP_Files[[8]], CP_Files[[9]], CP_Files[[10]], CP_Files[[11]], CP_Files[[12]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
CP_Data_VF <- CP_Data[, -c(7,8)]
colnames(CP_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
CP_Data_VF <- distinct(CP_Data_VF)

CP_Energy <- spread(CP_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(CP_Energy) <- CP_Energy[,1]
CP_Energy <- CP_Energy[,-1]
View(CP_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(CP_Energy) #630/630 miRNAs in raw FASTA file
nrow(CP_Energy) #2855/2855 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(CP_Energy, "./Exported_Tables/CP_Energy.csv")
```

# Species: Enterobacter cloacae (5393/5393 transcripts) 
First load in data files (22):
```{r}
EC_Files <- vector(mode = "list", length = 22)
EC_File_List <- list.files(path = "./Output_Files/ESKAPE/EC_ATCC", pattern = ".txt")

setwd("./Output_Files/ESKAPE/EC_ATCC")

for (i in 1:length(EC_Files)) {
  EC_Files[[i]] <- read.table(EC_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(EC_Files)
```

Then merge those data files into a single large table:
```{r}
EC_Data <- rbind(EC_Files[[1]], EC_Files[[2]], EC_Files[[3]], EC_Files[[4]], EC_Files[[5]], EC_Files[[6]], EC_Files[[7]], EC_Files[[8]], EC_Files[[9]], EC_Files[[10]], EC_Files[[11]], EC_Files[[12]], EC_Files[[13]], EC_Files[[14]], EC_Files[[15]], EC_Files[[16]], EC_Files[[17]], EC_Files[[18]], EC_Files[[19]], EC_Files[[20]], EC_Files[[21]], EC_Files[[22]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
EC_Data_VF <- EC_Data[, -c(7,8)]
colnames(EC_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
EC_Data_VF <- distinct(EC_Data_VF)

EC_Energy <- spread(EC_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(EC_Energy) <- EC_Energy[,1]
EC_Energy <- EC_Energy[,-1]
View(EC_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(EC_Energy) #630/630 miRNAs in raw FASTA file
nrow(EC_Energy) #5393/5393 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(EC_Energy, "./Exported_Tables/EC_Energy.csv")
```

# Species: Enterococcus faecium (2915/2915 transcripts)
First load in data files (12):
```{r}
EF_Files <- vector(mode = "list", length = 12)
EF_File_List <- list.files(path = "./Output_Files/ESKAPE/EF_DO", pattern = ".txt")

setwd("./Output_Files/ESKAPE/EF_DO")

for (i in 1:length(EF_Files)) {
  EF_Files[[i]] <- read.table(EF_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(EF_Files)
```

Then merge those data files into a single large table:
```{r}
EF_Data <- rbind(EF_Files[[1]], EF_Files[[2]], EF_Files[[3]], EF_Files[[4]], EF_Files[[5]], EF_Files[[6]], EF_Files[[7]], EF_Files[[8]], EF_Files[[9]], EF_Files[[10]], EF_Files[[11]], EF_Files[[12]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
EF_Data_VF <- EF_Data[, -c(7,8)]
colnames(EF_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
EF_Data_VF <- distinct(EF_Data_VF)

EF_Energy <- spread(EF_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(EF_Energy) <- EF_Energy[,1]
EF_Energy <- EF_Energy[,-1]
View(EF_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(EF_Energy) #630/630 miRNAs in raw FASTA file
nrow(EF_Energy) #2915/2915 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(EF_Energy, "./Exported_Tables/EF_Energy.csv")
```


# Species: Escherichia coli (4315/4315 transcripts)
First load in data files (17):
```{r}
EC_Files <- vector(mode = "list", length = 17)
EC_File_List <- list.files(path = "./Output_Files/EC", pattern = ".txt")

setwd("./Output_Files/EC")

for (i in 1:length(EC_Files)) {
  EC_Files[[i]] <- read.table(EC_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(EC_Files)
```

Then merge those data files into a single large table:
```{r}
EC_Data <- rbind(EC_Files[[1]], EC_Files[[2]], EC_Files[[3]], EC_Files[[4]], EC_Files[[5]], EC_Files[[6]], EC_Files[[7]], EC_Files[[8]], EC_Files[[9]], EC_Files[[10]], EC_Files[[11]], EC_Files[[12]], EC_Files[[13]], EC_Files[[14]], EC_Files[[15]], EC_Files[[16]], EC_Files[[17]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
EC_Data_VF <- EC_Data[, -c(7,8)]
colnames(EC_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
EC_Data_VF <- distinct(EC_Data_VF)

EC_Energy <- spread(EC_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(EC_Energy) <- EC_Energy[,1]
EC_Energy <- EC_Energy[,-1]
View(EC_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(EC_Energy) #630/630 miRNAs in raw FASTA file
nrow(EC_Energy) #4315/4315 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(EC_Energy, "./Exported_Tables/EC_Energy.csv")
```



# Species: Haemophilus influenza (1752/1752 transcripts)
First load in data files (7):
```{r}
HI_Files <- vector(mode = "list", length = 7)
HI_File_List <- list.files(path = "./Output_Files/HI", pattern = ".txt")

setwd("./Output_Files/HI")

for (i in 1:length(HI_Files)) {
  HI_Files[[i]] <- read.table(HI_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(HI_Files)
```

Then merge those data files into a single large table:
```{r}
HI_Data <- rbind(HI_Files[[1]], HI_Files[[2]], HI_Files[[3]], HI_Files[[4]], HI_Files[[5]], HI_Files[[6]], HI_Files[[7]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
HI_Data_VF <- HI_Data[, -c(7,8)]
colnames(HI_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
HI_Data_VF <- distinct(HI_Data_VF)

HI_Energy <- spread(HI_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(HI_Energy) <- HI_Energy[,1]
HI_Energy <- HI_Energy[,-1]
View(HI_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(HI_Energy) #630/630 miRNAs in raw FASTA file
nrow(HI_Energy) #1752/1752 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(HI_Energy, "./Exported_Tables/HI_Energy.csv")
```


# Species: Klebsiella pneumoniae (5458/5459 transcripts)
First load in data files (22):
```{r}
KP_Files <- vector(mode = "list", length = 22)
KP_File_List <- list.files(path = "./Output_Files/ESKAPE/KP_MGH", pattern = ".txt")

setwd("./Output_Files/ESKAPE/KP_MGH")

for (i in 1:length(KP_Files)) {
  KP_Files[[i]] <- read.table(KP_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(KP_Files)
```

Then merge those data files into a single large table:
```{r}
KP_Data <- rbind(KP_Files[[1]], KP_Files[[2]], KP_Files[[3]], KP_Files[[4]], KP_Files[[5]], KP_Files[[6]], KP_Files[[7]], KP_Files[[8]], KP_Files[[9]], KP_Files[[10]], KP_Files[[11]], KP_Files[[12]], KP_Files[[13]], KP_Files[[14]], KP_Files[[15]], KP_Files[[16]], KP_Files[[17]], KP_Files[[18]], KP_Files[[19]], KP_Files[[20]], KP_Files[[21]], KP_Files[[22]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
KP_Data_VF <- KP_Data[, -c(7,8)]
colnames(KP_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
KP_Data_VF <- distinct(KP_Data_VF)

KP_Energy <- spread(KP_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(KP_Energy) <- KP_Energy[,1]
KP_Energy <- KP_Energy[,-1]
View(KP_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(KP_Energy) #630/630 miRNAs in raw FASTA file
nrow(KP_Energy) #5458/5459 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(KP_Energy, "./Exported_Tables/KP_Energy.csv")
```





# Species: Mycobacterium abscessus (4972/4980 transcripts)
First load in data files (20):
```{r}
MA_Files <- vector(mode = "list", length = 20)
MA_File_List <- list.files(path = "./Output_Files/CF/MA_ATCC", pattern = ".txt")

setwd("./Output_Files/CF/MA_ATCC")

for (i in 1:length(MA_Files)) {
  MA_Files[[i]] <- read.table(MA_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(MA_Files)
```

Then merge those data files into a single large table:
```{r}
MA_Data <- rbind(MA_Files[[1]], MA_Files[[2]], MA_Files[[3]], MA_Files[[4]], MA_Files[[5]], MA_Files[[6]], MA_Files[[7]], MA_Files[[8]], MA_Files[[9]], MA_Files[[10]], MA_Files[[11]], MA_Files[[12]], MA_Files[[13]], MA_Files[[14]], MA_Files[[15]], MA_Files[[16]], MA_Files[[17]], MA_Files[[18]], MA_Files[[19]], MA_Files[[20]])


```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
MA_Data_VF <- MA_Data[, -c(7,8)]
colnames(MA_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
MA_Data_VF <- distinct(MA_Data_VF)

MA_Energy <- spread(MA_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(MA_Energy) <- MA_Energy[,1]
MA_Energy <- MA_Energy[,-1]
View(MA_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(MA_Energy) #630/630 miRNAs in raw FASTA file
nrow(MA_Energy) #4972/4980 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(MA_Energy, "./Exported_Tables/MA_Energy.csv")
```





# Species: Mycobacterium avium (5155/5155 transcripts)
First load in data files (21):
```{r}
MAv_Files <- vector(mode = "list", length = 21)
MAv_File_List <- list.files(path = "./Output_Files/MAv", pattern = ".txt")

setwd("./Output_Files/MAv")

for (i in 1:length(MAv_Files)) {
  MAv_Files[[i]] <- read.table(MAv_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(MAv_Files)
```

Then merge those data files into a single large table:
```{r}
MAv_Data <- rbind(MAv_Files[[1]], MAv_Files[[2]], MAv_Files[[3]], MAv_Files[[4]], MAv_Files[[5]], MAv_Files[[6]], MAv_Files[[7]], MAv_Files[[8]], MAv_Files[[9]], MAv_Files[[10]], MAv_Files[[11]], MAv_Files[[12]], MAv_Files[[13]], MAv_Files[[14]], MAv_Files[[15]], MAv_Files[[16]], MAv_Files[[17]], MAv_Files[[18]], MAv_Files[[19]], MAv_Files[[20]], MAv_Files[[21]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
MAv_Data_VF <- MAv_Data[, -c(7,8)]
colnames(MAv_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
MAv_Data_VF <- distinct(MAv_Data_VF)

MAv_Energy <- spread(MAv_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(MAv_Energy) <- MAv_Energy[,1]
MAv_Energy <- MAv_Energy[,-1]
View(MAv_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(MAv_Energy) #630/630 miRNAs in raw FASTA file
nrow(MAv_Energy) #5155/5155 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(MAv_Energy, "./Exported_Tables/MAv_Energy.csv")
```


# Species: Prevotella melaninogenica (2373/2391 transcripts)

First load in data files (10):
```{r}
PM_Files <- vector(mode = "list", length = 10)
PM_File_List <- list.files(path = "./Output_Files/PM/Complete", pattern = ".txt")

setwd("./Output_Files/PM/Complete")

for (i in 1:length(PM_Files)) {
  PM_Files[[i]] <- read.table(PM_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(PM_Files)
```

Then merge those data files into a single large table:
```{r}
PM_Data <- rbind(PM_Files[[1]], PM_Files[[2]], PM_Files[[3]], PM_Files[[4]], PM_Files[[5]], PM_Files[[6]], PM_Files[[7]], PM_Files[[8]], PM_Files[[9]], PM_Files[[10]])

```

Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
PM_Data_VF <- PM_Data[, -c(7,8)]
colnames(PM_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
PM_Data_VF <- distinct(PM_Data_VF)

PM_Energy <- spread(PM_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(PM_Energy) <- PM_Energy[,1]
PM_Energy <- PM_Energy[,-1]
View(PM_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(PM_Energy) #630/630 miRNAs in raw FASTA file
nrow(PM_Energy) #2373/2391 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(PM_Energy, "./Exported_Tables/PM_Energy.csv")
```


# Species: Pseudomonas aeruginosa (5555/5572 transcripts)

First load in data files (23):
```{r}
PA_Files <- vector(mode = "list", length = 23)
PA_File_List <- list.files(path = "./Output_Files/PA", pattern = ".txt")

setwd("./Output_Files/PA")

for (i in 1:length(PA_Files)) {
  PA_Files[[i]] <- read.table(PA_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(PA_Files)
```

Then merge those data files into a single large table:
```{r}
PA_Data <- rbind(PA_Files[[1]], PA_Files[[2]], PA_Files[[3]], PA_Files[[4]], PA_Files[[5]], PA_Files[[6]], PA_Files[[7]], PA_Files[[8]], PA_Files[[9]], PA_Files[[10]], PA_Files[[11]], PA_Files[[12]], PA_Files[[13]], PA_Files[[14]], PA_Files[[15]], PA_Files[[16]], PA_Files[[17]], PA_Files[[18]], PA_Files[[19]], PA_Files[[20]], PA_Files[[21]], PA_Files[[22]], PA_Files[[23]])
```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
PA_Data_VF <- PA_Data[, -c(7,8)]
colnames(PA_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
PA_Data_VF <- distinct(PA_Data_VF)

PA_Energy <- spread(PA_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(PA_Energy) <- PA_Energy[,1]
PA_Energy <- PA_Energy[,-1]
View(PA_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(PA_Energy) #630/630 miRNAs in raw FASTA file
nrow(PA_Energy) #5555/5572 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(PA_Energy, "./Exported_Tables/PA_Energy.csv")
```


# Species: Staphylococcus aureus (2767/2767 transcripts)

First load in data files (12):
```{r}
SA_Files <- vector(mode = "list", length = 12)
SA_File_List <- list.files(path = "./Output_Files/SA/Complete", pattern = ".txt")

setwd("./Output_Files/SA/Complete")

for (i in 1:length(SA_Files)) {
  SA_Files[[i]] <- read.table(SA_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(SA_Files)
```

Then merge those data files into a single large table:
```{r}
SA_Data <- rbind(SA_Files[[1]], SA_Files[[2]], SA_Files[[3]], SA_Files[[4]], SA_Files[[5]], SA_Files[[6]], SA_Files[[7]], SA_Files[[8]], SA_Files[[9]], SA_Files[[10]], SA_Files[[11]], SA_Files[[12]])


```

Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
SA_Data_VF <- SA_Data[, -c(7,8)]
colnames(SA_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
SA_Data_VF <- distinct(SA_Data_VF)

SA_Energy <- spread(SA_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(SA_Energy) <- SA_Energy[,1]
SA_Energy <- SA_Energy[,-1]
View(SA_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(SA_Energy) #630/630 miRNAs in raw FASTA file
nrow(SA_Energy) #2767/2767 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(SA_Energy, "./Exported_Tables/SA_Energy.csv")
```


# Species: Stenotrophomonas maltophilia (4417/4417)
First load in data files (18):
```{r}
SM_Files <- vector(mode = "list", length = 18)
SM_File_List <- list.files(path = "./Output_Files/SM", pattern = ".txt")

setwd("./Output_Files/SM")

for (i in 1:length(SM_Files)) {
  SM_Files[[i]] <- read.table(SM_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(SM_Files)
```

Then merge those data files into a single large table:
```{r}
SM_Data <- rbind(SM_Files[[1]], SM_Files[[2]], SM_Files[[3]], SM_Files[[4]], SM_Files[[5]], SM_Files[[6]], SM_Files[[7]], SM_Files[[8]], SM_Files[[9]], SM_Files[[10]], SM_Files[[11]], SM_Files[[12]], SM_Files[[13]], SM_Files[[14]], SM_Files[[15]], SM_Files[[16]], SM_Files[[17]], SM_Files[[18]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
SM_Data_VF <- SM_Data[, -c(7,8)]
colnames(SM_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
SM_Data_VF <- distinct(SM_Data_VF)

SM_Energy <- spread(SM_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(SM_Energy) <- SM_Energy[,1]
SM_Energy <- SM_Energy[,-1]
View(SM_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(SM_Energy) #630/630 miRNAs in raw FASTA file
nrow(SM_Energy) #4417/4417 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(SM_Energy, "./Exported_Tables/SM_Energy.csv")
```

# Species: Streptococcus parasanguinis (1974/1974 transcripts)
First load in data files (8):
```{r}
SP2_Files <- vector(mode = "list", length = 8)
SP2_File_List <- list.files(path = "./Output_Files/SP2", pattern = ".txt")

setwd("./Output_Files/SP2")

for (i in 1:length(SP2_Files)) {
  SP2_Files[[i]] <- read.table(SP2_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(SP2_Files)
```

Then merge those data files into a single large table:
```{r}
SP2_Data <- rbind(SP2_Files[[1]], SP2_Files[[2]], SP2_Files[[3]], SP2_Files[[4]], SP2_Files[[5]], SP2_Files[[6]], SP2_Files[[7]], SP2_Files[[8]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
SP2_Data_VF <- SP2_Data[, -c(7,8)]
colnames(SP2_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
SP2_Data_VF <- distinct(SP2_Data_VF)

SP2_Energy <- spread(SP2_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(SP2_Energy) <- SP2_Energy[,1]
SP2_Energy <- SP2_Energy[,-1]
View(SP2_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(SP2_Energy) #630/630 miRNAs in raw FASTA file
nrow(SP2_Energy) #1974/1974 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(SP2_Energy, "./Exported_Tables/SP2_Energy.csv")
```

# Species: Streptococcus pneumoniae (1998/1998 transcripts)
First load in data files (8):
```{r}
SP_Files <- vector(mode = "list", length = 8)
SP_File_List <- list.files(path = "./Output_Files/SP", pattern = ".txt")

setwd("./Output_Files/SP")

for (i in 1:length(SP_Files)) {
  SP_Files[[i]] <- read.table(SP_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(SP_Files)
```

Then merge those data files into a single large table:
```{r}
SP_Data <- rbind(SP_Files[[1]], SP_Files[[2]], SP_Files[[3]], SP_Files[[4]], SP_Files[[5]], SP_Files[[6]], SP_Files[[7]], SP_Files[[8]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
SP_Data_VF <- SP_Data[, -c(7,8)]
colnames(SP_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
SP_Data_VF <- distinct(SP_Data_VF)

SP_Energy <- spread(SP_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(SP_Energy) <- SP_Energy[,1]
SP_Energy <- SP_Energy[,-1]
View(SP_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(SP_Energy) #630/630 miRNAs in raw FASTA file
nrow(SP_Energy) #1998/1998 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(SP_Energy, "./Exported_Tables/SP_Energy.csv")
```

# Species: Streptococcus salivarius (1995/1995 transcripts)
First load in data files (8):
```{r}
SS2_Files <- vector(mode = "list", length = 8)
SS2_File_List <- list.files(path = "./Output_Files/SS2", pattern = ".txt")

setwd("./Output_Files/SS2")

for (i in 1:length(SS2_Files)) {
  SS2_Files[[i]] <- read.table(SS2_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(SS2_Files)
```

Then merge those data files into a single large table:
```{r}
SS2_Data <- rbind(SS2_Files[[1]], SS2_Files[[2]], SS2_Files[[3]], SS2_Files[[4]], SS2_Files[[5]], SS2_Files[[6]], SS2_Files[[7]], SS2_Files[[8]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
SS2_Data_VF <- SS2_Data[, -c(7,8)]
colnames(SS2_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
SS2_Data_VF <- distinct(SS2_Data_VF)

SS2_Energy <- spread(SS2_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(SS2_Energy) <- SS2_Energy[,1]
SS2_Energy <- SS2_Energy[,-1]
View(SS2_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(SS2_Energy) #630/630 miRNAs in raw FASTA file
nrow(SS2_Energy) #1995/1995 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(SS2_Energy, "./Exported_Tables/SS2_Energy.csv")
```

# Species: Streptococcus sanguinis (2265/2265 transcripts)
First load in data files (9):
```{r}
SS_Files <- vector(mode = "list", length = 9)
SS_File_List <- list.files(path = "./Output_Files/SS", pattern = ".txt")

setwd("./Output_Files/SS")

for (i in 1:length(SS_Files)) {
  SS_Files[[i]] <- read.table(SS_File_List[i],
        sep = ";", header = TRUE, quote = "")
}

View(SS_Files)
```

Then merge those data files into a single large table:
```{r}
SS_Data <- rbind(SS_Files[[1]], SS_Files[[2]], SS_Files[[3]], SS_Files[[4]], SS_Files[[5]], SS_Files[[6]], SS_Files[[7]], SS_Files[[8]], SS_Files[[9]])

```


Then restructure the data file and generate table of energy scores for individual miRNAs:
```{r}
SS_Data_VF <- SS_Data[, -c(7,8)]
colnames(SS_Data_VF) <- c("TargetGene", "start1", "end1", "miRNA", "start2", "end2", "Energy")
SS_Data_VF <- distinct(SS_Data_VF)

SS_Energy <- spread(SS_Data_VF[, c(1, 4, 7)], key = "miRNA", value = "Energy")
rownames(SS_Energy) <- SS_Energy[,1]
SS_Energy <- SS_Energy[,-1]
View(SS_Energy)

#Now test to make sure the data table is the right size (all miRNAs and transcripts are captured):
ncol(SS_Energy) #630/630 miRNAs in raw FASTA file
nrow(SS_Energy) #2265/2265 transcripts in raw FASTA file

#Now export to Exported_Tables folder
write.csv(SS_Energy, "./Exported_Tables/SS_Energy.csv")
```
